---
title: "IDS 572 Homework 4"
author: "Nabeel Khan, Nha Nguyen"
date: '2022-12-02'
output: pdf_document
---

```{r Load libraries}
#Import necessary packages
#install.packages('corrr')
#install.packages('nnet')
#install.packages('NeuralNetTools')
#install.packages("fastDummies")
#install.packages("caret")
#install.packages("neuralnet")
#install.packages("ROSE")
# Import necessary libraries 
library(readxl)
library(dplyr)
library(ggplot2)
library(tidyr)
library(corrr)
library(nnet)
library(NeuralNetTools)
library(fastDummies)
library(caret)
library(neuralnet)
library(ROSE)
```

```{r Load dataset}
data <- read_excel("/Users/hoangnha218/Desktop/IDS572 Homework 4/Assignment4Data.xlsx")
View(data)
```

```{r Question 1: Exploratory Data Analysis}
str(data) # 31 columns, 28 rows including 2 categorical and 26 numerical variables

#Remove unecessary columns
data <- data[, !names(data) %in% c("Fuel","Drs", "Cyl","Abag_1","ABS","PStr")]
data
# Check unique values
unique(data$Colour)

# Check missing values
sapply(data,function(x) sum(is.na(x)))

# Factor categorical variable
data$Colour <- as.factor(data$Colour)

# Check outliers with boxplot
boxplot(data,las=2.6,vertical = TRUE,main = "Boxplot of car data")

# Test relationship between categorical and numerical variables using Chi-squared test
chisq.test(data$Price, data$Colour)

# Compute the statistics of all numerical variables
summary(data)
```
#Key Insights:
#We remove the following columns because they don't affect our models' prediction output since the values of these columns remain the same for all records. The removed columns include "Fuel","Drs", "Cyl","Abag_1","ABS","PStr".
#There are no missing values in all columns.
#It can be observed that "Colour" is a categorical variable in the data. So, we need to factorize these variables.
#According to the boxplot, there are no significant outliers. 
#According to Pearson Chi-squared test, p value=0.235, greater than significance level (0.05), the variable "Colour" is not statistically significant.

#Question 1 Answers:
# The factors that influence a customer’s decision to buy a car are Horsepower (HP), Cylinder (CC), number of gear positions (Grs), Weight (Wght), Air Conditioning (AC) , Metallic Rim "M_rim" since their correlations with Price (target variable) are greater than 0.60, which refer to strong correlation. Their correlation coefficients are 0.92, 0.88, 0.76, 0.86, 0.62, 0.63 accordingly.

#What are the objectives of the model that Farid plans to build?
#...

``` {r Question 2 Neural Network Model}
#Scale data
mynormalization <- function(x)
{
  (x - min(x))/(max(x)-min(x))
}

nndata <- data %>% mutate_if(is.numeric, mynormalization)
summary(nndata)

# Split train test data
nnindx <- sample(2,nrow(nndata), replace = T, prob = c(0.7,0.3))
nntrain <- nndata[nnindx == 1,]
nntest <- nndata[nnindx ==2,]

# Build neural network model
nnModel <- nnet(Price ~ HP + CC + Grs + Wght + AC + M_Rim , data = nntrain, linout = F, size =10, decay = 0.01, maxit = 1000)
summary(nnModel)

# Plot the model
library(NeuralNetTools)
plotnet(nnModel)
```
```{r Question 2 NN Model Validation}
# Predictions on test data
nn.preds <- (predict(nnModel, nntest))

# Build confusion matrix
nnModel.CM <- table(nn.preds, nntest$Price, dnn = c("predicted", "actual"))
nnModel.CM

error <- function(nnModel.CM){
  TN = nnModel.CM[1,1]
  TP = nnModel.CM[2,2]
  FN = nnModel.CM[1,2]
  FP = nnModel.CM[2,1]
  recall = (TP)/(TP+FN)
  precision = (TP)/(TP+FP)
  error = (FP+FN)/(TP+TN+FN+FP)
  nnModel.perf <- list("precision" = precision,
                    "recall" = recall,
                    "error" = error)
  return(nnModel.perf)
}
output <- error(nnModel.CM)
output
```


``` {r Question 2 NN Model Interpretation with different hidden neurons}
nnindx2 <- sample(2,nrow(nntrain), replace = T, prob = c(0.5,0.3))
nntrain2 <- nntrain[nnindx2 == 1,]
nnvalidation <- nntrain[nnindx2 ==2,]
nnModel.err2 <- vector("numeric", 30)
d <- seq(0.0001, 1, length.out = 30)
k =1

for(i in d){
  model <- nnet(Price~ HP + CC + Grs + Wght + AC + M_Rim , data = nntrain2, decay=i, size=10, maxit=1000)
  nnpred.class <- (predict(model, nnvalidation))
  nnModel.err2[k] <- mean(nnpred.class!=nnvalidation$Price)
  k <- k+1
}
plotnet(model)
```


```{r Question 3 Linear Regression Model}

# Converting "Price" as numeric and factorize "Colour" variable
data$Price <- as.numeric(data$Price)
data$Colour <- as.factor(data$Colour)

mynormalization <- function(x)
{
  (x - min(x))/(max(x)-min(x))
}

lmdata<- data %>% mutate_if(is.numeric, mynormalization)
summary(lmdata)

# Split train test
set.seed(123)

lm.indx <- sample(2,nrow(lmdata), replace = T, prob = c(0.7,0.3))
lm.train <- lmdata[lm.indx == 1,]
lm.test <- lmdata[lm.indx ==2,]

full <- lm(lm.train$Price ~ .,data = lm.train)
null <- lm(lm.train$Price ~ 1,data = lm.train)

step(null, scope = list(lower = null, upper = full), direction = "forward", trace = 0)

lmModel <- lm(formula = lm.train$Price ~ HP + Colour+ Clock + Age  + Grs, data = lm.train)
summary(lmModel)

# LR prediction on test data
lm.pred <- predict(lmModel, newdata = lm.test)
#mean(lm.test$Price - pred.lm)^2
#fitted(lmModel)
#coefficients(lmModel)
#residuals((lmModel))

# LR Mean square error (MSE)
MSE.lm <- sum((lm.pred - lm.test$Price)^2)/nrow(lm.test)
MSE.lm
plot(lmModel)

```
``` {r Question 3 LR Model Validation}
#Error percentage
lm.error <- rmse(lm.test$Price, lm.pred)
lm.errorpercent <- lm.error/mean(lm.test$Price)
lm.errorpercent
```


#Comparing Neural Network Model and Linear Regression Model in automobile prediction
#...

#Question 4: Recommendation
#...